---
title: "Linear Model with prediction"
author: "Issa Darrouj"
date: "2025-10-29"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(tigerstats)
require(knitr)

data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE) 
```

### Model1: SIMS-ARM  

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```

```{r}
basicNN + geom_point() + ggtitle("SIMS vs ARM") + theme(plot.title = element_text(hjust = 0.5, size = 20))
```

### Numerical Results  

```{r}
cor(SIMS~ARM,data=data)
```


### Inferential Results  

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

### Create target  

```{r}
target <- data.frame(ARM=90, GRIP=90)
```

### Predict Target Point of Model 1

```{r}
predict(model.1,target,interval=c("prediction"))
```

### Linear Fit Model 1  

```{r}
basicNN + geom_point() + ggtitle("SIMS~ARM") + theme(plot.title = element_text(hjust = 0.5, size = 20)) + geom_smooth(method=lm)
```

### Model2: SIMS~GRIP

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=GRIP))
```

```{r}
basicNN + geom_point() + ggtitle("SIMS vs GRIP") + theme(plot.title = element_text(hjust = 0.5, size = 20))
```

### Numerical Results Model2

```{r}
cor(SIMS~GRIP,data=data)
```

### Inferential Results Model2

```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
```

### Predict Target Point for Model2

```{r}
predict(model.2,target,interval=c("prediction"))
```

### Linear Fit Model2

```{r}
basicNN + geom_point() + ggtitle("SIMS~GRIP") + theme(plot.title = element_text(hjust = 0.5, size = 20)) + geom_smooth(method=lm)
```

### Model3: SIMS~ARM+GRIP

### Numerical Results Model3  

```{r}
cor(SIMS~ARM+GRIP,data=data)
```

The correlation number for model3 (SIMS~ARM+GRIP) is higher compared to model2 (SIMS~GRIP) and model1 (SIMS~ARM), so the correlation is better when using both models (ARM and GRIP) rather than using one of them (either ARM or GRIP).

### Inferential Results Model3

```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.3)
```

The formula for getting Model3 is: formula = -5.433871 + 0.037311*ARM + 0.24470*GRIP

### Predict Target Point of Model3

```{r}
predict(model.1,target,interval=c("prediction"))
```

```{r}
predict(model.2,target,interval=c("prediction"))
```

```{r}
predict(model.3,target,interval=c("prediction"))
```

### Anova Test for Models

### Model1~Model3

```{r}
anova(model.1,model.3)
```

Our P-value was 0.000004994 which is very small. Which tells us that model3 is better than model 1 in a significant difference.

### Model2~Model3

```{r}
anova(model.2,model.3)
```

Our P-value for Models 2 and 3 (0.000000001495) is even smaller than the P-value of models 1 and 3 (0.000004994), which tells us that model 3 is the most accurate model out of the 3 models.